Trends in the contribution of major causes of death to the black-white life expectancy gap

### 2017-05-29 conferences/ResearchDay/Riddell_ResearchDay_minimal.Rmd
updated pres for HMD

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```
Jay Kaufman, Kathryn Morrison, and Sam Harper

@@

- When the number of deaths is between 1 and 9 it is <b class = "redtext">coarsened</b>.

@@

@@

@@

##Learn more
- Working paper submitted to bioRxiv - will be public soon!
- Shiny app hosted online with our results here:  https://corinne-riddell.shinyapps.io/shiny_app/

**Get in touch**

- corinne.riddell@mail.mcgill.ca
- @datavisitor on Twitter

>>>>

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```

Jay Kaufman, Kathryn Morrison, and Sam Harper

@@

@@

## The output

+ Working paper being screened at bioRxiv
+ R Shiny App: https://corinne-riddell.shinyapps.io/shiny_app/

## The app

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex1.gif")
```

## The app

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex2.gif")
```

## The app

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex3.gif")
```

@@

#Three examples

##CVD in men
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/CVD_men.png")
```

##Cancer in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Cancer_women.png")
```

##Injury in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Injury_women.png")
```

@@

##Get in touch
- corinne.riddell@mail.mcgill.ca
- @datavisitor on Twitter
